---
title: "NGS Analysis Basics_Sections123"
author: "Winston Wong"
date: "11/3/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

`biocLite()` function outdated, used `BiocManager` instead.
Bioconductor packages needed for tutorial:
```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")
BiocManager::install(version = "3.12")
```

Following packages were not installed properly: `KernSmooth`, `nlme`. Ran RStudio as administrator and installed packages accordingly.
```{r}
BiocManager::install(c("KernSmooth", "nlme"))
```

__3. Strings in R Base__

Generating a sample sequence data set:
```{r}
myseq <- c("ATGCAGACATAGTG", "ATGGAACATAGATCC", "GTACAGATCAC")
```

String searching with regular expression support: `grep()` searches for instances of `ATG` in the strings provided in `myseq`. `myseq[]` returns the strings found by `grep`.
```{r}
myseq[grep("ATG", myseq)]
```

Searches `myseq` for first match of pattern "AT": `regexpr()` function is used to identify where a pattern is within a character vector, where each element is searched separately; returns position of the 1st match.

```{r}
pos1 <- regexpr("AT", myseq)
as.numeric(pos1); attributes(pos1)$match.length #Returns position information of matches
```

Searches `myseq` for all matches of pattern "AT": `
```{r}
pos2 <- gregexpr("AT", myseq)
as.numeric(pos2[[1]]); attributes(pos2[[1]])$match.length # Returns positions of matches in first sequence
```

String substitution with regular expression support

```{r}
gsub("^ATG", "atg", myseq)
```

Positional parsing

```{r}
nchar(myseq) #computes length of strings

substring(myseq[1], c(1,3), c(2,5)) # Positional parsing of several fragments from one string

substring(myseq, c(1,4,7), c(2,6,10)) # Positional parsing of many strings (first string: 1-2, second string 4-6, third string 7-10)
```

RANDOM SEQUENCE GENERATION

Random DNA sequences of any length
```{r}
rand <- sapply(1:100,#length of vector
               function(x) paste(sample(c("A","T","G","C"), #function to be applied to each element of the vector
               sample(10:30), #maximum and minimum length of sequences
               replace=T), collapse=""))
rand[1:3] #Accesses first 3 sequences that are generated out of 100
```

Count identical sequences
```{r}
table(c(rand[1:4], rand[1])) #sequences within range ordered alphabetically, if second arguement is in range sequence appears with "2" beneath?
table(c(rand[1:4], rand[1]))
```

Extract reads from reference
```{r}
#installing package `Biostrings`
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")

BiocManager::install("Biostrings")

library(Biostrings)
library(dplyr)

ref <- sample(c("A","T","G","C"), 100000, replace=T) %>% paste(collapse="") %>% DNAString()

randstart <- sample(1:(length(ref)-15), 1000, replace = F) # sample() randomly reorders the elements passed as the first arguement 
randreads <- Views(ref, start = randstart, end = NULL, width=15)
rand_set <- DNAStringSet(randreads)
unlist(rand_set) #unlist a list of vectors into a single vector

```

