---
title: "NGS-Analysis-Basics-Section5"
author: "Winston Wong"
date: "11/29/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

__5. NGS Sequences__
Four lines per sequence:
1. ID
2. Sequence
3. ID
4. Base call qualities (Phred scores) as ASCII characters

The following gives an example of 3 Illuminia reads in a FASTQ file. The numbers at the beginning of each lines are not part of the FASTQ format. They have been added soley for illustration purposes.
```{r}
#1. @SRR038845.3 HWI-EAS038:6:1:0:1938 length=36
#2. CAACGAGTTCACACCTTGGCCGACAGGCCCGGGTAA
#3. +SRR038845.3 HWI-EAS038:6:1:0:1938 length=36
#4. BA@7>B=>:>>7@7@>>9=BAA?;>52;>:9=8.=A
#1. @SRR038845.41 HWI-EAS038:6:1:0:1474 length=36
#2. CCAATGATTTTTTTCCGTGTTTCAGAATACGGTTAA
#3. +SRR038845.41 HWI-EAS038:6:1:0:1474 length=36
#4. BCCBA@BB@BBBBAB@B9B@=BABA@A:@693:@B=
#1. @SRR038845.53 HWI-EAS038:6:1:1:360 length=36
#2. GTTCAAAAAGAACTAAATTGTGTCAATAGAAAACTC
#3. +SRR038845.53 HWI-EAS038:6:1:1:360 length=36
#4. BBCBBBBBB@@BAB?BBBBCBC>BBBAA8>BBBAA@
#Sequence and Quality Data
```

SEQUENCE AND QUALITY DATA: `QualityScaleXStringSet`
Phred quality scores are integers from 0-50 that are stored as ASCII characters after adding 33. The basic R functions `rawToChar` and `charToRaw` can be used to interconvert among their representations.

Phred score interconversion
```{r}
phred <- 1:9
phreda <- paste(sapply(as.raw((phred)+33), rawToChar), collapse="")
phreda
```

```{r}
as.integer(charToRaw(phreda))-33
```

